---
title: "College Admission Findings"
author: "The Four Leaf Clever"
output: 
  ioslides_presentation:
    logo: clover.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Background  

## Introduction  
Goals:  
1. Predict admission rates and find most influenctial variables.  
2. Develop a Shiny Web App for college consulting agency to use for evaluating changes to make to influence college admissions.  

## Data - Variables
Source: College Scorecard  
  
Some variables include:  
- State  
- Undergraduate student size  
- Undergraduate student race  
- Marital status  
- Percentage of first generation college  
- Average family income  
- SATs  


# Process  

## Method - Models  
To find the best model for prediction, following regression models were considered:

- Ordinary Least Squares Regression (OLS)
- Ridge Regression (RR)
- Lasso Regression (LR)
- Principal Components Regression (PCR)
- Partial Least Squares Regression (PLSR)  


# Analysis  

## Summary 
```{r echo = FALSE}
load("../data/RData-files/ols-regression.RData")
load("../data/RData-files/ridge-regression.RData")
load("../data/RData-files/Lasso-Regression.RData")
load("../data/RData-files/PCR-Regression.RData")
load("../data/RData-files/pls-regression.RData")

Regression <- c('OLS','Ridge', 'Lasso', 'PCR', 'PLSR')
MSE <- c(ols_MSE, ridge_MSE, lasso_tMSE, pcr_tMSE, pls_mse)
mse_chart <- data.frame(Regression, MSE)
```

```{r results="asis", echo = FALSE}
library(pander)
pander(mse_chart)
```

## App  
1. Input the school's OPEID in order to get information about the school  
2. Randomly choose 20 schools with a smaller admission rate and build a regression model using lasso regression  
3. Predict what our client's new admission rate is using the scaled data for our client's school as the inputs  
4. Output is an admission rate that is understandable and comparable with their current admission rate



